---
title: "Analysis for Project"
output: 
  html_document: 
    fig_height: 6
    fig_width: 9
    toc: yes
    toc_depth: 4
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
source("useful_functions.R")
load("output/analytical_data.RData")
library(ggplot2)
library(texreg)
library(MASS)

convertModel <- function(model) {
  tr <- createtexreg(
    coef.names = rownames(model$coef), 
    coef = model$coef$b.pool, 
    se = model$coef$se.pool, 
    pvalues = model$coef$pvalue.pool,
    gof.names = c("R2","BIC (null)","N"), 
    gof = c(model$r.squared, model$bic.null, model$n), 
    gof.decimal = c(T,F,F)
  )
}

```


```{r functions, echo=FALSE}
porl <- function(formula, imputations) 
  b <- se <- R2 <- NULL
  
  for(i in 1:imputations$m) 

    imputation <- complete(imputations, i)
    ```
    
    ```{r imputations, echo=FALSE}
imputations <- mice(pew, 5, printFlag=FALSE)
```

# Univariate plots Distributions
```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations, 1), 
       aes(x=american_perc, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Identity Perception") +
  xlab("Self Perception") + ylab("property")+
  theme_bw()
```

```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=culture_view, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Identity Perception") +
  xlab("Cultural Differences") + ylab("property")+
  theme_bw()
```



```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=minor_succe, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Identity Perception") +
  xlab("Successful Minority in the US") + ylab("property")+
  theme_bw()
```

```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=home_investment, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Perception of Buying a Home") +
  xlab("Buying a home is Long Term Investment in the US") + ylab("property")+
  theme_bw()
```

```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=exper_better_country, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Immigrants Experience: Treatment of the poor") +
  xlab("Treatment of the poor") + ylab("property")+
  theme_bw()
```

```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=exper_moral, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Immigrants Experience: the Moral Values of Society") +
  xlab("Moral Values of Society") + ylab("property")+
  theme_bw()
```

```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=exper_opportunity, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Immigrants Experience: the Opportunity to Get Ahead") +
  xlab("Opportunity to Get Ahead") + ylab("property")+
  theme_bw()
```



```{r figure 4, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(subset(pew, !is.na(home_own) & !is.na(exper_raising_child)), 
       aes(x=exper_raising_child, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Immigrants Experience: the Conditions for Raising Children") +
  xlab("Conditions for Raising Children") + ylab("property")+
  theme_bw()
```

```{r stargazer, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(complete(imputations,1),
       aes(x=exper_family_ties, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Immigrants Experience: the Strength of Family Ties") +
  xlab("Strength of Family Ties") + ylab("property")+
  theme_bw()
```

```{r figure test, echo=FALSE, fig.cap="", fig.align='center'}
ggplot(subset(pew, !is.na(home_own) & !is.na(exper_family_ties)), 
       aes(x=exper_family_ties, y=..prop.., group=1, fill=nativity))+
  geom_bar()+
  guides(fill=FALSE)+
  facet_grid(nativity~home_own)+
  ggtitle("Immigrants Experience: the Strength of Family Ties") +
  xlab("Strength of Family Ties") + ylab("property")+
  theme_bw()
```

```{r polr-experience}
model1<-polr(exper_better_country~home_own+nativity+I(age-40)+I((age-40)^2), data=imputation)
model2<- polr(exper_moral~home_own+nativity+I(age-40)+I((age-40)^2), data=imputation)
model3<- polr(exper_opportunity~home_own+nativity+I(age-40)+I((age-40)^2), data=imputation)
model4<- polr(exper_raising_child~home_own+nativity+I(age-40)+I((age-40)^2), data=imputation)
model5<- polr(exper_family_ties~home_own+nativity+I(age-40)+I((age-40)^2), data=imputation)
screenreg(list(model1, model2, model3, model4, model5), digits=5)

```

# Bivariate plots
<a href="#top">Back to top</a>

Use this R Markdown to perform the main analysis for the project. I use this basically as a lab notebook. It contains the main analysis and a variety of sensitivity analysis. The code in this documents serves as a baseline for the eventual tables and figures that will go into the paper. At the same time it will serve as a record of all supplementary analyses performed. 

```{r vote-generation, echo=FALSE, fig.cap="", fig.align='center'}
```
# Rune some models
```{r xxx-model, restult = 'asis'}
as.numeric(analytical_data$religion)
model <- lm()
htmlreg(model, 
        caption = "",
        caption.above = TRUE
        doctype = FALSE)
```

```{r polr-perception}
model6<- glm(american_perc~home_own+home_investment+I(age-40), data=imputation)
model7<- glm(american_perc~nativity+I(age-40), data=imputation)
model8<- glm(american_perc~home_own+nativity+I(age-40), data=imputation)
model9<- glm(american_perc~home_own+exper_moral+exper_opportunity+exper_raising_child+home_investment+nativity+I(age-40), data=imputation)


screenreg(list(model6, model7, model8, model9), digits=5)

```

```{r stargazer_example, results="asis", echo=FALSE, error=FALSE, message=FALSE}
model6 <- glm(american_perc~home_own+nativity+I(age-40)+I((age-40)^2), imputations)
model7 <- glm(american_perc~home_own+home_investment+nativity+I(age-40)+I((age-40)^2), imputations)
model8 <- glm(american_perc~home_own+exper_moral+exper_opportunity+exper_raising_child+exper_better_country+home_investment+nativity+I(age-40)+I((age-40)^2), imputations)
model9 <- glm(american_perc~exper_moral+exper_opportunity+exper_raising_child+exper_better_country+home_investment+nativity+I(age-40)+I((age-40)^2), imputations)


texreg(lapply(list(model6, model7, model8, model9), convertModel),
          custom.coef.names = c("Intercept",
                            "Own Home",
                             "Nativity",
                            "Age under 40",
                            "Age over 40",
                             "Moral Values of Society",
                             "Opportunity to Get Ahead",
                            "Condition of Raing Children",
                             "Treatment of the Poor"),
       caption="OLS regression models predicting Self Perception as American",
       caption.above = TRUE)

```
